\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2013-03-16 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
Made some corrections to manual and updated the pdf
added a comment about APPROXIMATE_OCEAN_LOAD; also fixed problems introduced by Lyx in the new fault dynamics section.

@@

@@

\begin{figure}[htbp]
\noindent \begin{centering}
\includegraphics[scale=0.3]{\lyxdot \lyxdot /src/MAIN_TRUNK/SPECFEM3D_Cartesian/doc/USER_MANUAL/figures/faultmesh}
\\
\includegraphics[scale=0.3]{\lyxdot \lyxdot /src/MAIN_TRUNK/SPECFEM3D_Cartesian/doc/USER_MANUAL/figures/surf168}
\includegraphics[scale=0.3]{\lyxdot \lyxdot /src/MAIN_TRUNK/SPECFEM3D_Cartesian/doc/USER_MANUAL/figures/splitnodes} 
\par\end{centering}

\caption{Screenshots of the CUBIT example for embedded fault with split nodes:
entire mesh decomposed into several volumes bounding the fault (top),
fault surface 168 is selected (bottom-left) and split nodes of the
fault illustrating only interior nodes of fault are split while those
on the edges of fault surface are touching each other (bottom-right).}

\label{fig:examples.splitnodes} 
\end{figure}

@@

(The user must number all the faults, starting at 1, with unit increments) 
\begin{lyxlist}{00.00.0000}
\item [{ids\_surf\_1}] list of Cubit ids of all surfaces that form side
1 of the fault
\item [{ids\_surf\_2}] list of Cubit ids of all surfaces that form side
2 of the fault 
\end{lyxlist}
(The user must decide which side of the fault is side 1. This choice
affects the sign conventions of fault quantities as explained in a
later section)\\

@@

The package includes examples, the SCEC benchmark problems: 
\begin{itemize}
\item TPV5, a planar vertical strike-slip fault 
\item TPV14 and TPV15, vertical strike-slip fault system with a fault branch 
\item TPV102 and TPV103, rate-and-state benchmarks
\item TPV16, heterogenous initial stress
\item Splay fault models from Wendt et al. (2009)\\

@@

\textbf{DATA/Par\_file} 
\begin{lyxlist}{00.00.0000}
\item [{\textbf{DATA/STATIONS}}] List of stations outside the fault 
\item [{\textbf{DATA/Par\_file\_faults}}] contains parameters of the fault.
The first part of this file has a strict format:

@@

\begin{lyxlist}{00.00.0000}
\item [{\&\textbf{INIT\_STRESS}}] input block sets the initial fault stresses
relative to the foot-wall side of the fault. Initial stresses are
composed of a constant background value possibly overwritten in prescribed
regions by heterogeneous distributions (see \&\textbf{DIST2D} blocks
below):

>>>>

\newenvironment{lyxlist}[1]
{\begin{list}{}
{\settowidth{\labelwidth}{#1}
\setlength{\leftmargin}{\labelwidth}
\addtolength{\leftmargin}{\labelsep}
\renewcommand{\makelabel}[1]{#1\hfil}}}
{\end{list}}

@@

If you want to model the effect of a fluid-solid model at short periods,
then set this flag to \texttt{.false.} and mesh the fluid layer explicitly in your mesher,
so that it is computed accurately and without this approximation.

@@

\begin{figure}[htbp]
\noindent \begin{centering}
\includegraphics[scale=0.3]{figures/faultmesh}
\\
\includegraphics[scale=0.3]{figures/surf168}
\includegraphics[scale=0.3]{figures/splitnodes}
\par\end{centering}
\caption{Screenshots of the CUBIT example for embedded fault with split nodes:
entire mesh decomposed into several volumes bounding the fault (top),
fault surface 168 is selected (bottom-left) and split nodes of the
fault illustrating only interior nodes of fault are split while those
on the edges of fault surface are touching each other (bottom-right).}
\label{fig:examples.splitnodes}
\end{figure}

@@

(The user must number all the faults, starting at 1, with unit increments)
\begin{lyxlist}{-}
\item [{ids\_surf\_1}] list of Cubit ids of all surfaces that form side
1 of the fault
\item [{ids\_surf\_2}] list of Cubit ids of all surfaces that form side
2 of the fault
\end{lyxlist}
(The user must decide which side of the fault is side 1. This choice
affects the sign conventions of fault quantities as explained in a
later section)\\

@@

The package includes examples, the SCEC benchmark problems:
\begin{itemize}
\item TPV5, a planar vertical strike-slip fault
\item TPV14 and TPV15, vertical strike-slip fault system with a fault branch
\item TPV102 and TPV103, rate-and-state benchmarks
\item TPV22 and TPV23, step-over benchmarks
\item TPV16, heterogenous initial stress
\item Splay fault models from Wendt et al. (2009)\\

@@

\textbf{DATA/Par\_file}
\begin{lyxlist}{-}
\item [{\textbf{DATA/STATIONS}}] List of stations outside the fault
\item [{\textbf{DATA/Par\_file\_faults}}] contains parameters of the fault.
The first part of this file has a strict format:

@@

\begin{lyxlist}{-}
\item [{\&\textbf{INIT\_STRESS}}] input block sets the initial fault stresses
relative to the foot-wall side of the fault. Initial stresses are
composed of a constant background value possibly overwritten in prescribed
regions by heterogeneous distributions (see \&\textbf{DIST2D} blocks
below):
